Models of Lambek calculus with subexponentials

### 2019-06-24 PaperDraft.tex
updates

  Let $\Sigma$ be a subexponential signature, then
  $SMALC_{\Sigma} \vdash \Gamma \rightarrow A \Rightarrow [\![\Gamma]\!] \leq [\![A]\!]$ for some valuation map $f$ and subexponential interpretation $\sigma : \Sigma \to CN(\mathcal{Q})$.
\end{theorem}

>>>>

  Let $\Sigma$ be a subexponential signature, then
  $SMALC_{\Sigma} \vdash \Gamma \rightarrow A \Rightarrow [\![\Gamma]\!] \leq [\![A]\!]$ for valuation map $f$ and for some subexponential interpretation $\sigma : \Sigma \to CN(\mathcal{Q})$.
\end{theorem}
